Viability of FTIR on fossil pollen

### 2020-10-06 manuscript.Rmd
added cross-ref with bookdown

---
title: 'Viability of FTIR on fossil pollen'
author: 'Florian Muthreich'
date: '2020/02/04'
output:
  pdf_document: default
bibliography: references.bib
---
# Notes
extracted fossil pollen from sediment.
ca 5 common taxa: Alnus, Picea, Pinus,

@@

9 depth from Dalmutladdo core. targeted and extracted Pinus pollen (see table)

@@

```{r}
dalmutladdo = data.frame(ID = c("DAL_08","DAL_20","DAL_40","DAL_60","DAL_90", "DAL_110","DAL_130","DAL_140","DAL_150"),
                         pinus_pollen = c(23,49,37,47,36,32,39,17,7),
                         alnus_pollen = c(0,7,0,0,0,0,0,0,0),
                         betula_pollen = c(0,15,0,0,0,0,0,0,0))
dalmutladdo
```

```{r}
fresh_pollen = data.frame(ID = c("BGO_PS7", "BGO_PS8", "INN_PS13", "INN_PS19A","NMBU_Pin_syl_14E1", "NMBU_Pin_syl_14H1", "NMBU_Aln_glu_14E1", "NMBU_Aln_glu_14J1", "NMBU_Aln_inc_14B1", "NMBU_Aln_inc_14G1", "NMBU_Bet_pub_14A1", "NMBU_Bet_pub_14B1", "NMBU_Cor_ave_14B1", "NMBU_Cor_ave_14C1"),
                          extracted = c(109,55,51,24,0,0,0,0,0,0,0,0,0,0))
fresh_pollen
```

>>>>

---
title: 'Viability of FTIR on fossil pollen'
author: 'Florian Muthreich'
date: '2020/02/04'
output:
  bookdown::pdf_document2:
    extra_dependencies: ["flafter"]
bibliography: references.bib
---

# Notes
extracted fossil pollen from sediment.
ca 5 common taxa: Alnus, Picea, Pinus,

@@

9 depth from Dalmutladdo core. targeted and extracted Pinus pollen (Table \@ref(tab:pollencounts), Table \@ref(tab:fresh))

@@

```{r pollencounts, echo=FALSE}
dalmutladdo = data.frame(ID = c("DAL_08","DAL_20","DAL_40","DAL_60","DAL_90", "DAL_110","DAL_130","DAL_140","DAL_150"),
                         pinus_pollen = c(23,49,37,47,36,32,39,17,7),
                         alnus_pollen = c(0,7,0,0,0,0,0,0,0),
                         betula_pollen = c(0,15,0,0,0,0,0,0,0))
knitr::kable(dalmutladdo, caption = "Pollen counts")
```

```{r fresh, echo=FALSE}
fresh_pollen = data.frame(ID = c("BGO_PS7", "BGO_PS8", "INN_PS13", "INN_PS19A","NMBU_Pin_syl_14E1", "NMBU_Pin_syl_14H1", "NMBU_Aln_glu_14E1", "NMBU_Aln_glu_14J1", "NMBU_Aln_inc_14B1", "NMBU_Aln_inc_14G1", "NMBU_Bet_pub_14A1", "NMBU_Bet_pub_14B1", "NMBU_Cor_ave_14B1", "NMBU_Cor_ave_14C1"),
                          extracted = c(109,55,51,24,0,0,0,0,0,0,0,0,0,0))
knitr::kable(fresh_pollen, caption = "Fresh pollen counts")
```
